NLTK: The Natural Language Toolkit

### 2002-03-20 technical/acl2002/submission.tex
- Added misc comments - Italicized design criteria (so they don't look so much like   other headings).
svn/trunk@515

% To do:
%   - FSA module description
%   - visualization modules description
%   - in-class demonstrations section
%   - Get rid of Python implementation section, or at least shorten it
%   - General clean-up
%   - ispell

@@

\noindent\textbf{Ease of Use.} The primary purpose of the toolkit is
to allow students to concentrate on building NLP systems.  The more
time students must spend learning to use the toolkit, the less useful
it is.

\noindent\textbf{Consistency.} The toolkit should use consistent data
structures and interfaces.

\noindent\textbf{Extensibility.} The toolkit should easily
accommodate new components, whether those components replicate or
extend the toolkit's existing functionality.  Thus, the toolkit's
design should be modular, with simple and well-defined interfaces
between modules.  The toolkit should also be structured in such a way
that it is obvious where new extensions would fit into the toolkit's
infrastructure.

\noindent\textbf{Documentation.} The toolkit, its data structures,
and its implementation all need to be documented.  Three documentation
types are necessary: technical reports, to explain the toolkit's
design and implementation; tutorials, to teach students how to use the
toolkit to perform specific tasks; and reference documentation, to
describe every module, interface, class and method.  All nomenclature
must be carefully chosen and consistently used.

@@

\noindent\textbf{Simplicity.} The toolkit should structure the
complexities of building NLP systems, not hide them.  Therefore, each
class defined by the toolkit should be simple enough that a student
could implement it by the time they finish the course.

\noindent\textbf{Modularity.} The interaction between different
components of the toolkit should be kept to a minimum.  In particular,
it should be possible to complete individual projects using small
parts of the toolkit, without worrying about how they interact with
the rest of the toolkit.  This will allow students to learn to use the
toolkit incrementally throughout the course.  Modularity also makes it
easier to change or extend the toolkit.

@@

\noindent\textbf{Comprehensiveness.} The toolkit is not intended to
provide a comprehensive set of tools.  Indeed, there should be a wide
variety of ways in which students can extend the toolkit.

\noindent\textbf{Efficiency.} The toolkit does not need to be highly
optimized for runtime performance.  However, it should be efficient
enough that students can use their NLP systems to perform real tasks.

\noindent\textbf{Cleverness.} Clear designs and implementations are
far preferable to ingenious yet indecipherable ones.

>>>>

% To do:
%   - Fill in OVERVIEW in the intro
%   - Write up evaluation
%   - Write up other approaches
%   - Write up conclusion
%   - Get rid of Python implementation section, or at least shorten it?
%   - General clean-up
%   - ispell

% We need more content on:
%   - documentation
%   - corpora?

@@

\noindent\textit{\textbf{Ease of Use.}} The primary purpose of the toolkit is
to allow students to concentrate on building NLP systems.  The more
time students must spend learning to use the toolkit, the less useful
it is.

\noindent\textit{\textbf{Consistency.}} The toolkit should use consistent data
structures and interfaces.

\noindent\textit{\textbf{Extensibility.}} The toolkit should easily
accommodate new components, whether those components replicate or
extend the toolkit's existing functionality.  Thus, the toolkit's
design should be modular, with simple and well-defined interfaces
between modules.  The toolkit should also be structured in such a way
that it is obvious where new extensions would fit into the toolkit's
infrastructure.

\noindent\textit{\textbf{Documentation.}} The toolkit, its data structures,
and its implementation all need to be documented.  Three documentation
types are necessary: technical reports, to explain the toolkit's
design and implementation; tutorials, to teach students how to use the
toolkit to perform specific tasks; and reference documentation, to
describe every module, interface, class and method.  All nomenclature
must be carefully chosen and consistently used.

@@

\noindent\textit{\textbf{Simplicity.}} The toolkit should structure the
complexities of building NLP systems, not hide them.  Therefore, each
class defined by the toolkit should be simple enough that a student
could implement it by the time they finish the course.

\noindent\textit{\textbf{Modularity.}} The interaction between different
components of the toolkit should be kept to a minimum.  In particular,
it should be possible to complete individual projects using small
parts of the toolkit, without worrying about how they interact with
the rest of the toolkit.  This will allow students to learn to use the
toolkit incrementally throughout the course.  Modularity also makes it
easier to change or extend the toolkit.

@@

\noindent\textit{\textbf{Comprehensiveness.}} The toolkit is not intended to
provide a comprehensive set of tools.  Indeed, there should be a wide
variety of ways in which students can extend the toolkit.

\noindent\textit{\textbf{Efficiency.}} The toolkit does not need to be highly
optimized for runtime performance.  However, it should be efficient
enough that students can use their NLP systems to perform real tasks.

\noindent\textit{\textbf{Cleverness.}} Clear designs and implementations are
far preferable to ingenious yet indecipherable ones.
